Approximation as Differentiation notes

### 2025-04-02 notes/sec/biproduct.tex
Enriched hom-functor.

Suppose $C$ a $\CMon$-enriched category. \todo{I think we can also define ``biproduct'' using a universal
property and zero morphisms, which might be nicer as we can then derive rather than assume $\CMon$-enrichment.}

>>>>

Suppose $C$ a $\CMon$-enriched category. \todo{I think we can also define ``biproduct'' just using zero
morphisms, and then derive rather than assume $\CMon$-enrichment.}

### 2025-04-02 notes/sec/cmon-enriched.tex
Enriched hom-functor.

Because $\CMon$ is closed monoidal, it is enriched over itself; every hom-object $\Hom{CMon}{A}{B}$ is a
commutative monoid where:

@@

\begin{definition}[$\mathscr{V}$-enriched functor]
For any monoidal category $(\mathscr{V}, \tensor, I)$ and $V$-enriched categories $C$ and $D$, a
\emph{$\mathscr{V}$-enriched} functor $F: C \to D$ on morphisms is a family of morphisms $F_{X,Y}:
\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between hom-objects in $\mathscr{V}$ that makes the following diagrams
in $\mathscr{V}$ commute:

@@

In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$ preserves the
additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

Suppose $C$ a small category. The usual \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $\Yoneda(X) = \Hom{C}{-}{X}: C \to \Set$ which
sends:
   \begin{itemize}
   \item any object $Y$ in $C$ to the hom-set $\Hom{C}{Y}{X}$;
   \item any morphism $f: Y \to Z$ in $C$ to the function $\Hom{C}{f}{X} = (- \comp f): \Hom{C}{Z}{X} \to
   \Hom{C}{Y}{X}$.
   \end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation $\Yoneda(f)$ where $\Yoneda(f)_Z = (f
\comp -): \Hom{C}{Z}{X} \to \Hom{C}{Z}{Y}$.
\end{itemize}

\noindent For a $\mathscr{V}$-enriched category $C$, the hom-functor $\Hom{C}{-}{X}: C \to \mathscr{V}$ is
$\mathscr{V}$-enriched.

\noindent For $\CMon$-enriched $C$, there is an enriched version of the Yoneda embedding, namely the
$\CMon$-enriched functor $\Yoneda_{\CMon}: C \to \Func{C^\op}{\CMon}_{\CMon}$. First we note that the
hom-functor $\Hom{C}{-}{X}: C \to \CMon$ is $\CMon$-enriched because composition is bilinear and so $(- \comp
f)$ preserves the additive structure of morphisms.

>>>>

Because $\CMon$ is closed monoidal, it is enriched over itself; every hom-object $\Hom{\CMon}{A}{B}$ is a
commutative monoid where:

@@

\begin{definition}[$\mathscr{V}$-enriched functor]
For any monoidal category $(\mathscr{V}, \tensor, I)$ and $\mathscr{V}$-enriched categories $C$ and $D$, a
\emph{$\mathscr{V}$-enriched} functor $F: C \to D$ on morphisms is a family of morphisms $F_{X,Y}:
\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between hom-objects in $\mathscr{V}$ that makes the following diagrams
in $\mathscr{V}$ commute:

@@

In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, enrichment means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual enriched functor properties.

@@

Suppose $C$ a small category. The usual \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $\Yoneda(X) = \Hom{C}{-}{X}: C^\op \to \Set$
which sends:
   \begin{itemize}
   \item any object $Y$ in $C$ to the hom-set $\Hom{C}{Y}{X}$;
   \item any morphism $f: Y \to Z$ in $C$ to the function $\Hom{C}{f}{X} = (- \comp f): \Hom{C}{Z}{X} \to
   \Hom{C}{Y}{X}$.
   \end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation $\Yoneda(f)$ where $\Yoneda(f)_Z = (f
\comp -): \Hom{C}{Z}{X} \to \Hom{C}{Z}{Y}$.
\end{itemize}

\noindent Now suppose $C$ is $\mathscr{V}$-enriched with $\mathscr{V}$ closed monoidal. Then the hom-functor
$\Hom{C}{-}{X}: C^\op \to \mathscr{V}$ is $\mathscr{V}$-enriched; the following diagram commutes by the
associativity of composition:

\begin{center}
\begin{tikzcd}[column sep=2.7cm]
   \Hom{C}{Y}{Z} \tensor \Hom{C}{X}{Y} \arrow[r, "\comp_{X,Y,Z}"] \arrow[d, "\Hom{C}{-}{W}_{Y,Z}\,\tensor\,\Hom{C}{-}{W}_{X,Y}"'] & \Hom{C}{X}{Z} \arrow[d, "\Hom{C}{-}{W}_{X,Z}"] \\
   \Hom{\mathscr{V}}{\Hom{C}{Z}{W}}{\Hom{C}{Y}{W}} \tensor \Hom{\mathscr{V}}{\Hom{C}{Y}{W}}{\Hom{C}{X}{W}} \arrow[r, "\comp_{\Hom{C}{X}{W},\Hom{C}{Y}{W},\Hom{C}{Z}{W}}"'] & \Hom{\mathscr{V}}{\Hom{C}{Z}{W}}{\Hom{C}{X}{W}}
\end{tikzcd}
\end{center}

\noindent \todo{Then there is an enriched version of the Yoneda embedding, namely a functor
$\Yoneda_{\mathscr{V}}: C \to \Func{C^\op}{\mathscr{V}}_{\mathscr{V}}$ analogous to the above which is itself
$\mathscr{V}$-enriched.}

% First we note that the hom-functor $\Hom{C}{-}{X}: C \to \CMon$ is $\CMon$-enriched because composition is
% bilinear and so $(- \comp f)$ preserves the additive structure of morphisms.
